---
title: "SLURM"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**SLURM** is a Hugo theme that adapts the **Xmin** theme. The original theme is intended to be e**X**tremely **MIN**imal. This extension is an attempt to be **S**lightly **L**ess **U**n**R**emittingly **M**inimal. My main goal though was to make sure I understand the basics of how Hugo works. 

## Getting started

To create the example site using the SLURM template into a fresh directory:

```{r, eval=FALSE}
blogdown::new_site(
  dir = "~/../Desktop/slurm", 
  theme = "djnavarro/hugo-slurm",
  theme_example = TRUE,
  sample = FALSE
)
```

By setting `theme_example = TRUE` (the default) it installs the example site, 
and by setting `sample = FALSE` it prevents Hugo from automatically including
the default content.

To serve an existing site, assuming that R the working directory is set to
the home directory for the site:

```{r, eval=FALSE}
blogdown::serve_site()
```






